### 2017-11-21 manuscript.rmd
started drafting intro

Siphonophores are...

>>>>

Siphonophores are a group of 188 valid species within Hydrozoa (Cnidaria), the vast majority of which are members of the plankton (fig. 1). Siphonophores are colonial, and are composed of zooids that are each homologous to solitary animals, but are physiologically integrated [@totton1965synopsis; @mackie1988siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial hydrozoans in terms of colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. A siphonophore colony arises from a single embryo, which forms a protozooid and a growth zone from which other genetically identical zooids bud asexually [@carre1969etude;@carre1991complete;@carre1967;@carre1995ordre]. Each zooid arises in the same repeating species-specific pattern, and is functionally specialized for a particular task (e.g feeding, reproducing, swimming) (fig 1A, B & C) [@dunn2006evolution].

Most siphonophores are planktonic, with the exception of one pleustonic species (*Physalia physalis*, Portuguese man of war) that lives at the interface of water and air, and a small clade of benthic siphonophores, the Rhodaliidae [@Totton1960;@pugh1983benthic].
